Novel Sampling Using Stochastic Gradient Descent

### 2016-12-05 poster/main.tex
finish the revision

\begin{itemize}
\item Sampling from posterior distribution is crucial in various statistical techniques
\item Posterior can be hard to sample  (hurdle a lot of applications)
\item SGD can be viewed as a Markov chain
\item Property as a Markov chain seems to be largely overlooked
\item Stationary distribution? Mixing time? Mixing time relationship with convergence rate?
\end{itemize}

@@

\begin{block}{SGD As Fast Posterior Sampler}
When $p(\theta)$ is the posterior distribution of some parameters given a set of data $X_1,\ldots, X_n$, i.e.,
\[
p(\theta) = \prod_{i=1}^n P(X_i|\theta) P(\theta),
\]
The noisy gradient step in Algorithm 1 can be estimated by subsampling:
\begin{theorem}[Central limit theorem]
Let $K$ be the subsampling size and $\eta_1,\ldots, \eta_K$ be samples drawing from $1,\ldots, n$ with replacement, then
\[
K^{-1}\sum_{i=1}^K (\nabla \log P(X_{\eta_i}|\theta^t) - \log P(\theta^t)) \sim \N(n^{-1} \nabla \log p(\theta) , K^{-1}\cov \nabla \log p(\theta)).
\]
\end{theorem}

>>>>

\begin{itemize}
\item Sampling from posterior distribution is crucial in various statistical techniques
\item Posterior can be hard to sample  (hurdle a lot of applications)
\item SGD can be viewed as a Markov chain sampler, very efficient for posterior
\item Property as a Markov chain largely overlooked
\item Mixing time's relationship with its convergence rate?
\end{itemize}

@@

\begin{block}{SGD As Fast Posterior Sampler}
When $p(\theta)$ is the posterior distribution of some parameters given a set of data $X_1,\ldots, X_n$, i.e.,
\[
p(\theta) = \prod_{i=1}^n P(X_i|\theta) P(\theta),
\]
The noisy gradient step in Algorithm 1 can be estimated by subsampling:
(Central limit theorem)
Let $K$ be the subsampling size and $\eta_1,\ldots, \eta_K$ be samples drawing from $1,\ldots, n$ with replacement, then
\[
K^{-1}\sum_{i=1}^K (\nabla \log P(X_{\eta_i}|\theta^t) - \log P(\theta^t)) \sim \N(n^{-1} \nabla \log p(\theta) , K^{-1}\cov \nabla \log p(\theta)).
\]
